---
title: "NLR_A results output"
author: "Charlotte Woolley"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning=FALSE)
knitr::opts_chunk$set(message=FALSE)
knitr::opts_chunk$set(fig.align='center')

options(scipen=999)

```


```{r, include = FALSE}

#LIBRARIES:
  library(evaluate)

#Perform the method 
replay(evaluate(file("/Users/s1576473/dev/growth_cleanR/data_cleaning_methods/NLR_A.R")))
```

*Overall Summary of Data After Error and Duplication Simulation (and before cleaning)*

Total induced errors = `r sum(dat$induced_error == TRUE)`

Total induced duplications = `r sum(dat$duplications == TRUE)`

Total induced complete duplications = `r sum(dat$complete_duplications == TRUE)`

Mean = `r mean(dat$new_weight)`

Median = `r median(dat$new_weight)`

SD = `r sd(dat$new_weight)`

Range = `r range(dat$new_weight)`

Number of observations = `r length(factor(dat$ind_ID))`

Number of individuals =  `r length(unique(factor(dat$ind_ID)))`


*Graph of data before NLR_A method*

```{r}
ggplot(dat, aes(x = age/365, y = new_weight, group = ind_ID, colour = sex, fill= sex)) +
                geom_line(alpha = 0.4, lwd = 0.2) +
                geom_point(alpha = 0.4) +
                labs(x = "Age (years)", 
                     y = "Weight (kg)") +
                scale_x_continuous(breaks = c(0,5,10,15,20,25,30,35,40,45,50,55,60,65,70,75,80,85,90,95,100)) +
                scale_y_log10(breaks=c(0.1,0.2,0.5,1,2,5,10,20,50,100,200,500,1000,2000,5000,10000,20000,50000,100000,200000),
                              labels=c(0.1,0.2,0.5,1,2,5,10,20,50,100,200,500,1000,2000,5000,10000,20000,50000,100000,200000)) +
                theme_bw() +
               theme(axis.title.y = element_text(face="bold", size=12), 
                      axis.text.y  = element_text(size=12),
                      axis.title.x = element_text(face="bold", size=12),
                      axis.text.x  = element_text(size=12),
                      plot.title = element_text(face="bold", size=12, hjust = 0.5),
                      legend.title = element_blank(), 
                      legend.text = element_text(face="bold", size=12),
                      legend.position = c(0.85, 0.1))
```



```{r}
#DELETIONS
  deletions <- subset(dat, !(dat$row_ID %in% master_NLR_A$row_ID)) 

#percentage of data deleted
  del <- 100 - ((length(master_NLR_A$ind_ID)/length(dat$ind_ID))*100)

#ALGORITHM DELETIONS (ONLY RELEVANT TO NLR-A AND NLME-A METHODS!)
if(exists("dat3") == TRUE) {
#jumping deletions 
  deletions_4 <- subset(dat3, !(dat3$row_ID %in% dat4$row_ID))
}
if(exists("dat3") == FALSE) {
  deletions_4 <- as.data.frame(NA)
}

if(exists("dat4") == TRUE) {
#impluasible values deletions 
  deletions_5 <- subset(dat4, !(dat4$row_ID %in% master_NLR_A$row_ID))
}

if(exists("dat4") == FALSE) {
  deletions_5 <- as.data.frame(NA)
}
  
#MODIFICATIONS
  master_NLR_A <- master_NLR_A %>% 
    mutate(changed_weight = weight != new_weight)
  
  modifications <- subset(master_NLR_A,master_NLR_A$changed_weight == TRUE) 
  

  mod_div10 <- subset(modifications, 
                      modifications$div10_weights_outlier == FALSE & 
                        modifications$div10_smallest_diff == TRUE) 
  
  mod_div100 <- subset(modifications, 
                       modifications$div100_weights_outlier == FALSE &
                       modifications$div100_smallest_diff == TRUE) 
  
  mod_div1000 <- subset(modifications, 
                        modifications$div1000_weights_outlier == FALSE & 
                          modifications$div1000_smallest_diff == TRUE) 
  
  mod_mul10 <- subset(modifications, 
                      modifications$mul10_weights_outlier == FALSE & 
                        modifications$mul10_smallest_diff == TRUE) 
  
  mod_mul100 <- subset(modifications, 
                       modifications$mul100_weights_outlier == FALSE & 
                         modifications$mul100_smallest_diff == TRUE) 
  
  mod_mul1000 <- subset(modifications, 
                        modifications$mul1000_weights_outlier == FALSE & 
                          modifications$mul1000_smallest_diff == TRUE)
  
  mod_min100 <- subset(modifications, 
                       modifications$min100_weights_outlier == FALSE & 
                         modifications$min100_smallest_diff == TRUE) 
  
  mod_min1000 <- subset(modifications, 
                        modifications$min1000_weights_outlier == FALSE & 
                          modifications$min1000_smallest_diff == TRUE) 
  
  mod_add100 <- subset(modifications, 
                       modifications$add100_weights_outlier == FALSE & 
                         modifications$add100_smallest_diff == TRUE)
  
  mod_add1000 <- subset(modifications, 
                        modifications$add1000_weights_outlier == FALSE & 
                          modifications$add1000_smallest_diff == TRUE) 
  
  mod_kgs <- subset(modifications, 
                    modifications$kg_weights_outlier == FALSE & 
                      modifications$kg_smallest_diff == TRUE) 
  
  mod_lbs <- subset(modifications,  
                    modifications$lbs_weights_outlier == FALSE & 
                      modifications$lbs_smallest_diff == TRUE) 
  
  mod_rev <- subset(modifications, 
                    modifications$reversed_weights_outlier == FALSE & 
                      modifications$reversed_smallest_diff == TRUE) 
        
#Sensitivity and Specificity

        induced_errors <- subset(dat, dat$induced_error == TRUE)
        #Total number of errors
        te <- length(induced_errors$row_ID)
        #Total number of errors modified or deleted
        tec <- sum(deletions$induced_error == TRUE) +
          sum(modifications$induced_error == TRUE)
        
        #Sensitivity of method
        se <- tec/te*100
        
        not_induced_errors <- subset(dat, dat$induced_error == FALSE)
        #Total number of non-errors
        tne <- length(not_induced_errors$row_ID)
        #Total number of non-errors NOT corrected or deleted
        tnec <- tne - (sum(deletions$induced_error == FALSE & deletions$complete_duplications == FALSE) +
          sum(modifications$induced_error == FALSE & modifications$complete_duplications == FALSE))
        
        #Specificity of method
        sp <- tnec/tne*100

```


*Overall Summary of NLR_A Method Performance (after data cleaning)*


Mean = `r mean(master_NLR_A$new_weight)`

Median = `r median(master_NLR_A$new_weight)`

SD = `r sd(master_NLR_A$new_weight)`

Range = `r range(master_NLR_A$new_weight)`

Number of observations = `r length(factor(master_NLR_A$ind_ID))`

Number of individuals =  `r length(unique(factor(master_NLR_A$ind_ID)))`

Sensitivity =  `r se`

Specificity =  `r sp`

Total deletions =  `r length(deletions$ind_ID)`

Percentage deleted = `r del`

Complete duplications deletions (or step 1 of algorithm) = `r sum(deletions$complete_duplications)`

Non-complete (identical) duplications deletions (or step 2 of algorithm) = `r sum(deletions$complete_duplications == FALSE & deletions$duplications == TRUE)`

Total modifications (or step 3 of algorithm) = `r length(modifications$ind_ID)`

Add 100 modifications = `r length(mod_add100$ind_ID)`

Add 1000 modifications = `r length(mod_add1000$ind_ID)`

Subtract 100 modifications = `r length(mod_min100$ind_ID)`

Subtract 1000 modifications  = `r length(mod_min1000$ind_ID)`

Multiply by 10 modifications = `r length(mod_mul10$ind_ID)`

Multiply by 100 modifications = `r length(mod_mul100$ind_ID)`

Multiply by 1000 modifications = `r length(mod_mul1000$ind_ID)`

Divide by 10 modifications = `r length(mod_div10$ind_ID)`

Divide by 100 modifications = `r length(mod_div100$ind_ID)`

Divide by 1000 modifications = `r length(mod_div1000$ind_ID)`

Convert to kg modifications = `r length(mod_kgs$ind_ID)`

Convert to lbs modifications = `r length(mod_lbs$ind_ID)`

Transpose modifications = `r length(mod_rev$ind_ID)`

Jumping measurements deletions (or step 4 of algorithm) = `r length(deletions_4$ind_ID)`

Implausible measurements deletions (or step 5 of algorithm) = `r length(deletions_5$ind_ID)`


*Graph of data after NLR_A method*

```{r}
ggplot(master_NLR_A, aes(x = age/365, y = new_weight, group = ind_ID, colour = sex, fill= sex)) +
                geom_line(alpha = 0.4, lwd = 0.2) +
                geom_point(alpha = 0.4) +
                labs(title = "Cleaned weight data", 
                     x = "Age (years)", 
                     y = "Weight (kg)") +
             scale_x_continuous(breaks = c(0,5,10,15,20,25,30,35,40,45,50,55,60,65,70,75,80,85,90,95,100)) +
                scale_y_continuous() +
                theme_bw() +
               theme(axis.title.y = element_text(face="bold", size=12), 
                      axis.text.y  = element_text(size=12),
                      axis.title.x = element_text(face="bold", size=12),
                      axis.text.x  = element_text(size=12),
                      plot.title = element_text(face="bold", size=12, hjust = 0.5),
                      legend.title = element_blank(), 
                      legend.text = element_text(face="bold", size=12),
                      legend.position = c(0.85, 0.1))
```





